A Summery about reasoning with logic

### 2015-10-27 reasoning/summery.tex
added more texts, made a crazy text on how to proof

So there are 2 kinds of proving. The first one is writing a proof in the system
this should be rather easy, although you have to be carefull to follow the
rules to the letter. I'm going to ignore this one since its just using the
rules, which you've done tons of times as a programmer, so it shouldn't be
that strange.

@@

First you have soundness, then there is completness, and finally you can be
asked to proof certain properties of a system.

@@

@@

@@

\subsection{Induction}
\label{induction}

@@

\noindent
\begin{tabular}{@{}ll@{}}
Symbols&
In natural language \\ \toprule
$\vdash$ 					& Part of system \\
$\vdash, \Rightarrow$ 		& Seperator between antecedent and succedent\\ \bottomrule
\end{tabular}

\section{Systems}
\begin{itemize}
	\item $H$  Hilbert, has a huge set of axioms, and only 1 rule. (also called fredge)
	\item $CPC$ Clasicial Propositional logic, formulas in here are always true
(tautologies)
	\item $GKC$ Gentzen calculus, also called sequent calcules
	\item $GKC_K$  Getnzen + R 
\end{itemize}

>>>>

So there are 2 kinds of proving. The first one is writing a proof in the system
this should be rather easy, although you have to be carefull to follow the
rules to the letter. I'm going to ignore this one since its just using the
rules, which you've done tons of times as a programmer, so it shouldn't be
that strange. Although I'm making an exception for Hilbert and Grammar,
Hilbert isn't that obvious and Grammar isn't obvious either.

@@

First you have soundness, then there is completness, these are both just
properties of a system, so there are many more things to proof, but these
are some of the most important because they decide if a system is usable.

@@

The technical defintion is: The argument should be valid and all
its premisses are true. Premisses in a system are the axioms.
So they should be valid (valution function returns 1). The arguments
in a system are the rules, so they should at least preserve truth.

@@

\section{proving completeness}
Every validity should be proofable in the system. So there is usually no 
obvious way of proving this, but for the system treated in the course
there are some

@@

\subsection{Induction}
\label{induction}
In here you try to prove something by starting with a single case n.

For all n (*), n=1, supose (*) for n, then show (*) for n+1.

So you start with an assumption, usually based on the question.
For example \emph{show that if $\vdash_x A$ then A is a bird.}

So you start with the base case, ie: \emph{We assume that $\vdash_x A$}
You can do this because of propositional logic, whenever you see
if x then y or x implies y you can just assume x. Continuing:
\emph{Which means there is a proof $A_1,\ldots,A_n$ of A}.
Here you're just saying that because A is part of X, there consists
a bunch of steps that lead to A. \emph{We prove$A_i$ is a
`birdlike property' with induction to $i$} Here you're saying
that the steps that lead to A have all `birdlike properties' (or whatever
property you're using) and you're gonna use induction to show that.
\emph{As $A_n = A$ this implies A is a `birdlike poperty'}

Now you're using the properties of the system and you call them lemmas.
These are the arguments and you connect them to the semantic.
\emph{Lemma 1, we have to proof that all axioms are `birdlike properties'
	This is done by showing with help of the semantics of x, in case of
system x this is a sleeve.
Bellow you can see the sleeve of axiom D which clearly indicates that
axiom D is birdlike
}

\[sleevefigure\]

\emph{For axiom Z you can also see its birdlike:}
\[(slightly altered) sleevefigure\]

You do this for all the axioms.

The next lemma is about the rules, these also have to be shown to keep
track of birdlikeness in system x:

\emph{Lemma 2, all the rules of x preserve birdlikeness:
	For the rule argument ad hominum, supose that the precedents
	are bird like
}
Precedents are the stuff you put into the rule.
You can supose this because you've already shown in lemma 1 all the axioms are
birdlike, so for the induction step it can't be anything else.
\emph{
	With the following sleeve it is shown that not under all valuations 
	birdlikeness is preserved, but only for the ones were birdlikeness was
	already there
}
\[(uninteresting) sleevefigure\]

\emph{this finises the proof for lemma 2}

Now the final step of induction is doing the induction step with help of the
just proven lemmas.

\subsection{tabloo or truth tree}
In this strategy you create a tree, starting from the axioms which is either
true or false, you go down step by step and say what happens. In most systems
if one of the axioms is false it means the conclusion is false to.

@@

\noindent
\begin{tabular}{@{}ll@{}}
Symbols&
In natural language \\ \toprule
$\vdash$ 					& Part of system, ie, is derivable \\
$\vdash, \Rightarrow$ 		& Seperator between antecedent and succedent\\ \bottomrule
\end{tabular}

\section{Systems}
\begin{itemize}
	\item $H$  Hilbert, has a huge set of axioms, and only 1 rule. (also called fredge)
	\item $CPC$ Clasicial Propositional logic, formulas in here are always true
(tautologies)
	\item $GKC$ Gentzen calculus, also called sequent calcules
	\item $GKC_K$  Getnzen + R 
	\item $GKP$ Genzen + structural rules.
\end{itemize}

\section{Proving in Hilbert}
Hilbert is the most simple system. However because of its simplicity proving
things in it isn't very obvious. There are multiple ways of writing proovs

\section{Proving in Grammar Logic}
Grammar logic is a (failed) attempt to make sense of natural langauge. It
tries to organize words into types, and groups of those words into compositional
types.
Connection words such as ` that' will have complex types.
